Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

Our analysis of the survey results can inform several potential avenues for
future research. For instance, the rollout of extensive videoconferencing and
virtual teaching solutions that the COVID pandemic has brought has also taught
us a series of lessons: it increases isolation and decreases the amount of
synchronous contact that happens in the fringes of the classroom (e.g.  teaching
staff offices, or before and after class). A future line of research could focus
on these issues and explore how chatbot technology could address them.

>>>>

Our analysis of the survey results can inform several potential avenues for
future research. For instance, the rollout of extensive videoconferencing and
virtual teaching solutions that the COVID-19 pandemic has brought has also taught
us a series of lessons: it increases isolation and decreases the amount of
synchronous contact that happens in the fringes of the classroom (e.g.  teaching
staff offices, or before and after class). A future line of research could focus
on these issues and explore how chatbot technology could address them.
